%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\cvsection{Work Experience}
\begin{cventries}

	\cventry
	{Graduate Intern}
	{Truveta}
	{Seattle, WA}
	{May 2021 - May 2022}
	{\begin{cvitems}
			\item {Developed a toolkit to measure data quality of Truveta Health Data Model (THDM), garnering trusts from health providers. Contributed to new partnerships with multiple after Private Review in Aug 2021, and with Microsoft in Sept 2021.}
			% \item {Designed a Monte Carlo sampling model to generate synthetic patient data for stress-testing.}
			\item {Established the foundation approach and model for Synthetic Patient Health Data, helps identify bottleneck in ETL process of EHR.}
			% , involving probabilistic theory of document retrieval, representation (feature) learning and deep learning. The model will not only help with generation of Synthetic Health Data, but also be implemented in filling missing patient data, predict doctor-patient encounter from health history, etc.
			\item {Developed an annotation recommender system for medical concept normalization. Reduced internal annotators' workload by 80\%}
			\item {Deployed cost-effective and scalable SOTA Named Entity Recognition (NER) Models for clinical notes information extraction. Saved \$2 million in cost compared to existing third party solutions, and optimized to reduce 75\% operating cost overhead compared with original baseline}
			% \item {}
			% \item {Assisted team members and other co-workers on various Projects and Collaborative efforts.}
		\end{cvitems}}
	\cventry
	{Teaching Assistant}
	{Florida Tech - Dept. of Mathematical Sciences}
	{Melbourne, FL}
	{August 2018 - December 2021}
	{\begin{cvitems}
			\item {Teached and graded exams for Probability \& Statistics, Neural Networks, Calculus I, II, III.}
			\item {Aided students studying Stochastic Modeling, Differential Equations.}
		\end{cvitems}}
	\cventry
	{IBM Data Science Practitioner - Instructor}
	{IBM Skill Academy}
	{}
	{May 2021 - June 2021}
	{\begin{cvitems}
			\item {Earned Certification for Instructor role for IBM Data Science Practitioner.}
			\item {Audited IBM Data Science learning material and proposed changes that was added to the material.}
			\item {Created a curriculum for teaching IBM Data Science course at Florida Tech.}
		\end{cvitems}}
\end{cventries}
\vspace{-4mm}