%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Projects}
\begin{cventries}

	\cventry
	{Apply Persistent Homology (TDA) for feature engineering. 91\% testing accuracy with shallow net.}
	{Classification of Extended MNIST Handwritten Digits and Letters Dataset}
	{giotto-ai, sklearn, Tensorflow}
	{\href{https://colab.research.google.com/drive/18z161k3diYO6sNVBfiKH8uGqbrekxMPN?usp=sharing}{[Project link]}}
	{}
	\vspace{-6mm}
	
	% \cventry
	% {Feature engineering image representation (MFCC) of audio data. 91\% validation accuracy with ensemble}
	% {Google Speech Command Classification}
	% {MFCC, Tensorflow}
	% {\href{https://colab.research.google.com/drive/1KCJjwgW6VDlANLmXYTotatk2xux3nw0N?usp=sharing}{[Project link]}}
	% {}
	% \vspace{-6mm}
	
	\cventry
	{Datamine, ETL to extract user review from MAL. Predict user rating based on data-mined review text with sentiment analysis. 94\% testing accuracy with ensemble model}
	{Sentiment Analysis on MyAnimeList User Ratings}
	{Redis, Docker, Tensorflow}
	{\href{https://github.com/n0k0m3/rnn-mal-sentiment}{[Project link]}}
	{}
	\vspace{-6mm}
	
	\cventry
	{Data analysis Container with Jupyter notebook server with GPU-RAPIDS AI for GPU-accelerated data transformation, Spark/Pyspark for distributed and scalable ETL, with addition of all common data science libraries. Aiming for feature parity with Databricks while staying minimal.}
	{GPU PySpark Notebook with DeltaLake}
	{Docker, Compose, Github CD/CI}
	{\href{https://github.com/n0k0m3/pyspark-notebook-deltalake-docker}{[Repo link]}}
	{}
	\vspace{-6mm}
	
	\cventry
	{Reverse Engineered game for assets decryption. Cron Pipeline for continuous update and decrypt data.}
	{Date A Live: Spirit Pledge Assets Decryption tool}
	{frida, ghidra, Github CD/CI}
	{\href{https://github.com/n0k0m3/DALSP-Assets-Decryption-tool}{[Repo link]},\href{https://github.com/n0k0m3/DateALiveData}{[Data link]}}
	{}
	\vspace{-10mm}
	
\end{cventries}