%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, letterpaper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
% \colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}
% \definecolor{sectiondivider}{HTML}{5D5D5D}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[circle,noedge,left]{./examples/profile}
\name{Van Minh}{Nguyen}
% \position{Site Reliability Engineer{\enskip\cdotp\enskip}Software Architect}
\address{Melbourne, FL, USA}

% \mobile{(+1) 321-368-9310}
\email{vmnguyen251@gmail.com}
%\dateofbirth{January 1st, 1970}
\homepage{n0k0m3.github.io}
\github{n0k0m3}
\linkedin{minhnguyen251}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \kaggle{kaggle-id}
% \hackerrank{hackerrank-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra information}

% \quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {UF Information Technology Hiring Team}
  {University of Florida\\Gainesville, FL 32611}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for AI Support Engineer}
% How the letter is opened
\letteropening{Dear UFIT Hiring Team,}
% How the letter is closed
\letterclosing{Best regards,}
% Any enclosures with the letter
% \letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal information
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Van Minh Nguyen~~~·~~~Cover Letter}
  {}

% Print the title with above letter information
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

  I am thrilled to apply for the AI Support Engineer position within UF Information Technology's Research Computing unit. As a Ph.D. candidate in Operations Research at Florida Tech with a strong background in AI/ML research and development, I am confident I have the skills and experience to make a significant impact in this role.

  What attracts me most to this opportunity is the chance to support UF's innovative researchers across diverse domains by developing efficient workflows and solutions on the powerful HiPerGator supercomputer. I am excited by the prospect of collaborating with the UFIT team to design new features and services that meet researchers' evolving needs.
  Some key strengths I would bring to this role include:

  \begin{itemize}
    \item   Extensive experience with Linux distributions (CentOS, Ubuntu), Python programming, and AI/ML frameworks
    \item   Hands-on knowledge of SLURM scheduling, having utilized FIT's SLURM HPC cluster extensively for research
    \item   Proven ability to thrive in fast-paced, collaborative environments and effectively communicate technical concepts to diverse audiences, as demonstrated during my Truveta internships
    \item   Strong problem-solving and workflow optimization skills, exemplified by my work on scalable NER pipelines that led to \$2M in annual cloud cost savings at Truveta
  \end{itemize}
  
  
  I am particularly eager to apply my background in advanced AI research - spanning satellite 3D reconstruction, suicide prevention, and deep reinforcement learning - to support UF's groundbreaking projects. The opportunity to work with world-class faculty, students, and collaborators to solve real-world challenges is incredibly energizing.

  I believe my technical skills, passion for AI innovation, and drive to support research excellence make me a strong fit for this role. I would welcome the chance to further discuss how I could contribute to UFIT's mission of empowering UF's research community.

  Thank you for considering my application. I look forward to the possibility of joining the UFIT team and advancing UF's remarkable research and education efforts.
\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
\makeletterclosing

\end{document}
