%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, letterpaper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Color definitions
\input{color.tex}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
\input{resume/personal_information.tex}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Company Recruitment Team}
  {Google Inc.\\1600 Amphitheatre Parkway\\Mountain View, CA 94043}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Software Engineer}
% How the letter is opened
\letteropening{Dear Mr./Ms./Dr. LastName,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
% \letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal information
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Van Minh Nguyen~~~·~~~Cover Letter}
  {}

% Print the title with above letter information
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

    Dear Hiring Manager,
    I am writing to express my strong interest in joining your team as an AI Support Engineer. With a Ph.D. in Operations Research from Florida Tech and extensive experience in AI/ML research and development, I believe I would be a valuable asset to your organization.
    Throughout my academic and professional journey, I have honed my skills in Python, C++, and various Linux distributions, as well as big data and cloud platforms like Spark, Azure, and Kubernetes. I have a proven track record of thriving in fast-paced, collaborative environments and delivering impactful projects that align with stakeholder needs.
    Some key highlights of my experience include:
    
    Initiating and implementing an on-premise Kubernetes server cluster for the Neural Transmissions Lab at FIT
    Developing scalable Named Entity Recognition (NER) pipelines and optimizing cloud infrastructure costs during my internship at Truveta, resulting in \$2M annual savings
    Conducting cutting-edge research in satellite 3D reconstruction, suicide prevention, and deep reinforcement learning for robotics
    
    I am excited about the opportunity to bring my technical expertise, problem-solving skills, and passion for AI to your team. I believe my background in both research and industry settings has prepared me well to contribute to your organization's mission and success.
    Thank you for your consideration. I look forward to the possibility of further discussing my qualifications and how I can contribute to your team.

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
\makeletterclosing

\end{document}
