%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has brveen downloaded from:
% http://www.LaTeXTemplates.com

%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage{multicol}
\usepackage{hyperref}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Van Minh Nguyen} % Your name
\address{Melbourne, FL USA} % Your address
\address{\href{https://www.linkedin.com/in/minhnguyen251/}{LinkedIn Link}, \href{https://github.com/n0k0m3/}{GitHub Link}} % LinkedIn URL
\address{(321)-368-9310 \\ vmnguyen251@gmail.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	MISSION STATEMENT/CAREER OBJECTIVE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Career Objective}
    Highly motivated, exceptionally fast learner Graduate student in Operations Research looking to advance into a career in Data Sciences/Analytics.
    % Experienced with SIMD optimization with NumPy, distributed computing with Spark/PySpark, various Deep Learning platforms (Tensorflow, Pytorch, Microsoft ONNX) and ML libraries (RapidsAI, Scikit-learn, ).
    Aiming to utilize my academic and internship experience to breach the wall between theoretical mathematics (especially in Topological Data Analysis) and real-world applications.\\
    Currently interested in learning about topological dimensionality reduction for data processing.
\end{rSection}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

% \begin{rSection}{Objective}
% To broaden skills in software development and %establish a basis for future employment in Japan.
% \end{rSection}

\begin{rSection}{Education}

    {\bf Florida Institute of Technology, Melbourne FL}
    \\ Ph.D Operations Research  GPA: 4.00 \hfill {\em Aug 2020 - Present}
    \\ M.S. Operations Research  GPA: 4.00 \hfill {\em Aug 2018 - May 2020}
    \\ B.S. Biochemistry (Biology Emphasis)    GPA: 3.43\hfill {\em Aug 2014 - May 2018}
\end{rSection}

%{\bf Courses}
%\\Algorithms \& Data Structures, Parallel Processing, Database Systems, Discrete Mathematics, Abstract Algebra, Combinatorics \& Graph Theory, Formal Languages \& Automata Theory, Java (3 Semesters), C++ (2 Semesters), FORTRAN, Numerical Analysis, Optimization, Linear Algebra.


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

    \begin{rSubsection}{Florida Institute of Technology - Dept. of Mathematical Sciences}{\em August 2018 - Present}{Graduate Student/Teaching Assistant}{}
        \item Research on Double Stochastic Processes (Branching Process with random offsprings)
        \item Teach and grade exams for Calculus I, II, III
        \item Tutor and grade exams for Probability \& Statistics, Neural Networks.
        \item Aid students studying Stochastic Modeling, Differential Equations
    \end{rSubsection}

    \begin{rSubsection}{Truveta}{\em May 2021 - August 2021}{Graduate Intern}{}
        \item Developed a data quality measurement toolkit, with \textbf{Databrick} and \textbf{PySpark}, to measure data quality of Truveta Health Data Model (THDM), garnering trusts from health providers.
        \item Designed a Monte Carlo sampling model to generate synthetic patient data for stress-testing.
        \item Established the foundation approach for (new) Synthetic Patient Health Data, involving probabilistic theory of document retrieval, representation (feature) learning and deep learning.
        % The model will not only help with generation of Synthetic Health Data, but also be implemented in filling missing patient data, predict doctor-patient encounter from health history, etc.
        \item Developed an annotation recommender system for THDM medical concept normalization.
        \item Assisted team members and other co-workers on various Projects and Collaborative efforts.
    \end{rSubsection}

    \begin{rSubsection}{IBM Skill Academy}{\em May 2021 - June 2021}{IBM Data Science Practitioner - Instructor}{}
        \item Earned Certification for Instructor role for IBM Data Science Practitioner
        \item Audited IBM Data Science learning material and proposed changes that was added to the material.
        \item Created a curriculum for teaching IBM Data Science course at Florida Institute of Technology
    \end{rSubsection}


\end{rSection}

\begin{rSection}{Projects}
    \begin{rSubsection}{Classification of Extended MNIST Handwritten Digits and Letters Dataset}{}{\href{https://colab.research.google.com/drive/18z161k3diYO6sNVBfiKH8uGqbrekxMPN?usp=sharing}{Project link}}{}
        \item EMNIST dataset is MNIST (handwritten digit) dataset with handwritten characters
        \item Applied Principal Component Analysis (PCA) and Persistent Homology (TDA) to reduce the dimension of dataset. Reduced feature size from 784 (28x28) to 35 while retaining 99\% variance
        \item Utilized libraries \textbf{giotto-ai} along-side standard deep learning libraries \textbf{sklearn, NumPy, Tensorflow}
        \item Achieved 97\%-91\% training-testing accuracy with a tuned network with only 3 hidden layers
    \end{rSubsection}

    \begin{rSubsection}{Google Speech Command Dataset Classification}{}{\href{https://colab.research.google.com/drive/1KCJjwgW6VDlANLmXYTotatk2xux3nw0N?usp=sharing}{Project link}}{}
        \item Classify Google Speech Command using Convolutional Neural Network on audio data (CNN)
        \item Pipeline processing audio data to image features with data augmentation
        \item Used multiple CNN architectures (LeNet, MiniGoogleNet, AlexNet) for training and stacking model for ensemble.
        \item Achieved 91\% validation accuracy with stacking model for ensemble.
    \end{rSubsection}

    \begin{rSubsection}{Sentiment Analysis on MyAnimeList User Ratings}{}{\href{https://github.com/n0k0m3/rnn-mal-sentiment}{Repo link}, \href{https://colab.research.google.com/github/n0k0m3/rnn-mal-sentiment/blob/main/main.ipynb}{Project link}}{}
        \item Predict user rating based on review using Recurrent Neural Network (RNN)
        \item Setup a data-mining pipeline utilizing self-hosted REST API with a \textbf{Redis} server for caching inside \textbf{dockerized} container
        \item Used different models (RNN with LSTM, CNN, CNN with Word2Vec embedding layers) for training and stacking model for ensemble.
        \item Achieved 94\% validation accuracy with ensemble model
    \end{rSubsection}

    \begin{rSubsection}{Movie Ratings Analysis}{}{}{}
        \item Initiate a Jupyter-Python notebook environment using \textbf{Amazon AWS EC Instance}
        \item Pre-processed/cleaned movie rating data extracted from IMDB.
        \item Import data to \textbf{SQL} database hosted on \textbf{Amazon AWS RDS} and ran queries to analyze user trends.
    \end{rSubsection}

    \begin{rSubsection}{Date A Live: Spirit Pledge Assets Decryption tool}{}{Personal Project. \href{https://github.com/n0k0m3/DALSP-Assets-Decryption-tool}{Repo link}}{}
        \item Reverse Engineer mobile game Date A Live: Spirit Pledge using Static analysis tool from NSA \textbf{ghidra} and dynamic analysis tool \textbf{frida}.
        \item Re-implement decryption functions using Python, implement methods to convert PowerVR, Ericsson Texture Compression format to digital images format (JPEG/PNG)
        \item Data-mined to find insecure API/server that allows easy download/extraction of new game contents.
    \end{rSubsection}
    \begin{rSubsection}{Other Minor Projects}{}{Personal Project. \href{https://github.com/n0k0m3}{GitHub link}}{}
        \item Reverse engineer mobile game Arknights to find AES256 key for assets decryption. \href{https://github.com/n0k0m3/Arknights-Lua-Decrypter}{Repo link}
        \item Maintained a toolkit that patches (cheats) mobile game Azur Lane. Added both 32/64-bit capability to the tool, features that allows user to obtain ingame paywalled contents for free while avoid cheating detection. \href{https://github.com/n0k0m3/Azur-Lane-Scripts-Autopatcher}{Repo link}
        \item Date A Live: Spirit Pledge Datamining repository using developed decryption tool. Using \textbf{cronjob} and \textbf{Github Action CI/CD} to automate fetch, decrypt and datamine new contents. \href{https://github.com/n0k0m3/DateALiveData}{Repo link}
    \end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------



\begin{rSection}{Skills}

    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{5ex}} l }
        %Teaching \\ 
        Software \& Tools & Python, Spark/PySpark, MySQL, Redis, Tensorflow, PyTorch, ONNX        \\
        Operating Systems & Windows, Linux, UNIX-based (MacOS)                                    \\
        Skills            & Data Processing \& Analysis, Stochastic Modeling, Reverse Engineering \\
        Languages         & Vietnamese (Native), English (Fluent), Japanese (Basic)
    \end{tabular}
\end{rSection}

\begin{rSection}{Academic Honors}
    \begin{rSubsection}{}{}{}{}
        \item Dean's List for Spring 2016, Fall 2017, Spring 2018 (GPA $\geq$ 3.7)
        \item Member of \textbf{Phi Kappa Phi} Honor Society (top 10\% percent of graduate students on campus)
    \end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
% Extra Curricular
%----------------------------------------------------------------------------------------

\begin{rSection}{Personal Traits}
    \begin{rSubsection}{}{}{}{}
        \item Enjoys adopting cutting edge technologies, especially in Deep Learning and Automation.
        \item Passionate and innovative researcher.
        \item Highly motivated, fast learner with exceptional multi-tasking skills.
        \item Love clearing up jargons with easy-to-understand concepts.
    \end{rSubsection}
\end{rSection}



\end{document}