%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

    \begin{rSubsection}{Florida Institute of Technology - Dept. of Mathematical Sciences}{\em August 2018 - Present}{Graduate Student/Teaching Assistant}{}
        \item Researched on Double Stochastic Processes (Branching Process with random offsprings)
        \item Researching Electronics Health Record embeddings for Machine Learning/Deep Learning
        \item Teached and grade exams for Calculus I, II, III
        \item Tutored and grade exams for Probability \& Statistics, Neural Networks.
        \item Aided students studying Stochastic Modeling, Differential Equations
    \end{rSubsection}

    \begin{rSubsection}{Truveta}{\em May 2021 - August 2021}{Graduate Intern}{}
        \item Developed a data quality measurement toolkit, with \textbf{Databrick} and \textbf{PySpark}, to measure data quality of Truveta Health Data Model (THDM), garnering trusts from health providers.
        \item Designed a Monte Carlo sampling model to generate synthetic patient data for stress-testing.
        \item Established the foundation approach for (new) Synthetic Patient Health Data, involving probabilistic theory of document retrieval, representation (feature) learning and deep learning.
        % The model will not only help with generation of Synthetic Health Data, but also be implemented in filling missing patient data, predict doctor-patient encounter from health history, etc.
        \item Developed an annotation recommender system for THDM medical concept normalization.
        \item Assisted team members and other co-workers on various Projects and Collaborative efforts.
    \end{rSubsection}

    \begin{rSubsection}{IBM Skill Academy}{\em May 2021 - June 2021}{IBM Data Science Practitioner - Instructor}{}
        \item Earned Certification for Instructor role for IBM Data Science Practitioner
        \item Audited IBM Data Science learning material and proposed changes that was added to the material.
        \item Created a curriculum for teaching IBM Data Science course at Florida Institute of Technology
    \end{rSubsection}


\end{rSection}