\begin{rSection}{Projects}
    \begin{rSubsection}{Classification of Extended MNIST Handwritten Digits and Letters Dataset}{}{\href{https://colab.research.google.com/drive/18z161k3diYO6sNVBfiKH8uGqbrekxMPN?usp=sharing}{Project link}}{}
        \item EMNIST dataset is MNIST (handwritten digit) dataset with handwritten characters
        \item Applied Principal Component Analysis (PCA) and Persistent Homology (TDA) to reduce the dimension of dataset. Reduced feature size from 784 (28x28) to 35 while retaining 99\% variance
        \item Utilized libraries \textbf{giotto-ai} along-side standard deep learning libraries \textbf{sklearn, NumPy, Tensorflow}
        \item Achieved 97\%-91\% training-testing accuracy with a tuned network with only 3 hidden layers
    \end{rSubsection}

    \begin{rSubsection}{Google Speech Command Dataset Classification}{}{\href{https://colab.research.google.com/drive/1KCJjwgW6VDlANLmXYTotatk2xux3nw0N?usp=sharing}{Project link}}{}
        \item Classify Google Speech Command using Convolutional Neural Network on audio data (CNN)
        \item Pipeline processing audio data to image features with data augmentation
        \item Used multiple CNN architectures (LeNet, MiniGoogleNet, AlexNet) for training and stacking model for ensemble.
        \item Achieved 91\% validation accuracy with stacking model for ensemble.
    \end{rSubsection}

    \begin{rSubsection}{Sentiment Analysis on MyAnimeList User Ratings}{}{\href{https://github.com/n0k0m3/rnn-mal-sentiment}{Repo link}, \href{https://colab.research.google.com/github/n0k0m3/rnn-mal-sentiment/blob/main/main.ipynb}{Project link}}{}
        \item Predict user rating based on review using Recurrent Neural Network (RNN)
        \item Setup a data-mining pipeline utilizing self-hosted REST API with a \textbf{Redis} server for caching inside \textbf{dockerized} container
        \item Used different models (RNN with LSTM, CNN, CNN with Word2Vec embedding layers) for training and stacking model for ensemble.
        \item Achieved 94\% validation accuracy with ensemble model
    \end{rSubsection}

    \begin{rSubsection}{Movie Ratings Analysis}{}{}{}
        \item Initiate a Jupyter-Python notebook environment using \textbf{Amazon AWS EC Instance}
        \item Pre-processed/cleaned movie rating data extracted from IMDB.
        \item Import data to \textbf{SQL} database hosted on \textbf{Amazon AWS RDS} and ran queries to analyze user trends.
    \end{rSubsection}

\begin{SWE}
    \begin{rSubsection}{Date A Live: Spirit Pledge Assets Decryption tool}{}{Personal Project. \href{https://github.com/n0k0m3/DALSP-Assets-Decryption-tool}{Repo link}}{}
        \item Reverse Engineer mobile game Date A Live: Spirit Pledge using Static analysis tool from NSA \textbf{ghidra} and dynamic analysis tool \textbf{frida}.
        \item Re-implement decryption functions using Python, implement methods to convert PowerVR, Ericsson Texture Compression format to digital images format (JPEG/PNG)
        \item Data-mined to find insecure API/server that allows easy download/extraction of new game contents.
    \end{rSubsection}
    \begin{rSubsection}{Other Minor Projects}{}{Personal Project. \href{https://github.com/n0k0m3}{GitHub link}}{}
        \item Reverse engineer mobile game Arknights to find AES256 key for assets decryption. \href{https://github.com/n0k0m3/Arknights-Lua-Decrypter}{Repo link}
        \item Maintained a toolkit that patches (cheats) mobile game Azur Lane. Added both 32/64-bit capability to the tool, features that allows user to obtain ingame paywalled contents for free while avoid cheating detection. \href{https://github.com/n0k0m3/Azur-Lane-Scripts-Autopatcher}{Repo link}
        \item Date A Live: Spirit Pledge Datamining repository using developed decryption tool. Using \textbf{cronjob} and \textbf{Github Action CI/CD} to automate fetch, decrypt and datamine new contents. \href{https://github.com/n0k0m3/DateALiveData}{Repo link}
    \end{rSubsection}
\end{SWE}

\end{rSection}