%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\vspace{-4mm}
\cvsection{Work Experience}
\vspace{-2mm}
\begin{cventries}

	\cventry
	{DevOps Engineer - Neural Transmissions Lab}
	{Florida Tech}
	{Melbourne, FL}
	{Jan 2022 - Present}
	{\begin{cvitems}
			\item {Deploy and maintain on-premise bare-metal servers for research lab.}
			\item {Deploy multi-user research/development environments with GPU support for deep learning.}
			\item {Deploy Zero Trust Architecture for granting role-based access (RBAC) to servers: authentication with Keycloak and SAML, authorization with Google OAuth and OpenLDAP.}
			\item {Secure deployments with HTTPS for web server, with proper DNS configuration, short-lived SSH certs for remote access, and VNC over HTTPS for remote control.}
		\end{cvitems}}

	\vspace{-2mm}

	\cventry
	{Teaching Assistant - Department of Mathematical Sciences}
	{}
	{}
	{Aug 2018 - Dec 2022}
	{\begin{cvitems}
			\item {Taught and graded exams for Probability \& Statistics, Neural Networks, Calculus I, II, III.}
			\item {Aided students studying Stochastic Modeling and Theory of Stochastic Processes.}
			\item {Technical support for students learning Neural Networks and Machine Learning.}
		\end{cvitems}}

	\vspace{-1mm}

	\cventry
	{Research Intern}
	{Truveta}
	{Seattle, WA}
	{Jan 2022 - May 2022}
	{\begin{cvitems}
			\item {Cost-effective and scalable SOTA Named Entity Recognition (NER) pipelines for clinical notes information extraction and de-identification. Saved \$2 million in annual cost, and further optimized to reduce 75\% operating cost overhead compared with original baseline model.}
			\item {Prototyped clinical notes annotation tool for internal annotator team.}
			\item {Threat modeling and mitigation for deployment of mentioned tools, including common attack vectors on platform and PHI leakage threats.}
		\end{cvitems}}

	\vspace{-2mm}

	\cventry
	{Graduate Intern}
	{}
	{}
	{May 2021 - Aug 2021}
	{\begin{cvitems}
			\item {Developed an ETL pipeline to measure data quality of Truveta Health Data Model (THDM), garnering trusts from health providers. Contributed to new partnerships with multiple after Private Review in Aug 2021, and with Microsoft in Sept 2021.}
			\item {Designed a synthetic patient data model for stress-testing and identify bottleneck in ETL process.}
			% \item {Established the foundation approach and model for Synthetic Patient Health Data}
			% , involving probabilistic theory of document retrieval, representation (feature) learning and deep learning. The model will not only help with generation of Synthetic Health Data, but also be implemented in filling missing patient data, predict doctor-patient encounter from health history, etc.
			\item {Developed an annotation recommender system for medical concept normalization. Reduced internal annotators' workload by 80\%}
			% \item {}
			% \item {Assisted team members and other co-workers on various Projects and Collaborative efforts.}
		\end{cvitems}}

	% \vspace{-4mm}

	% \cventry
	% {Graduate Intern}
	% {Truveta}
	% {Seattle, WA}
	% {May 2021 - Aug 2021}
	% {\begin{cvitems}
	% 		\item {Developed an ETL pipeline to measure data quality of Truveta Health Data Model (THDM), garnering trusts from health providers. Contributed to new partnerships with multiple after Private Review in Aug 2021, and with Microsoft in Sept 2021.}
	% 		\item {Designed a synthetic patient data model for stress-testing and identify bottleneck in ETL process.}
	% 		% \item {Established the foundation approach and model for Synthetic Patient Health Data}
	% 		% , involving probabilistic theory of document retrieval, representation (feature) learning and deep learning. The model will not only help with generation of Synthetic Health Data, but also be implemented in filling missing patient data, predict doctor-patient encounter from health history, etc.
	% 		\item {Developed an annotation recommender system for medical concept normalization. Reduced internal annotators' workload by 80\%}
	% 		% \item {}
	% 		% \item {Assisted team members and other co-workers on various Projects and Collaborative efforts.}
	% 	\end{cvitems}}

	% \cventry
	% {IBM Data Science Practitioner - Instructor}
	% {IBM Skill Academy}
	% {}
	% {May 2021 - June 2021}
	% {\begin{cvitems}
	% 		\item {Earned Certification for Instructor role for IBM Data Science Practitioner.}
	% 		\item {Audited IBM Data Science learning material and proposed changes that was added to the material.}
	% 		\item {Created a curriculum for teaching IBM Data Science course at Florida Tech.}
	% 	\end{cvitems}}

\end{cventries}